External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-08 CVPR2017_Review_Unified.tex
add

Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images. The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images. The impact is that the image details will be lost or hardly visible. As a result, image denoising is an essential procedure for the reliability of these vision systems. In the research area, image denoising is an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.

For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and most of them focus mainly on dealing with additive white Gaussian noise (AWGN). In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.). The models designed for AWGN would become much less effective on real noisy images.

>>>>

%Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images. The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images. The impact is that the image details will be lost or hardly visible. As a result,

Image denoising is an essential procedure for the reliability of many vision systems such as medical imaging and surveillance. It is also an ideal platform for testing computer vision models. Image denoising is to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise. For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning}, and most of them focus on additive white Gaussian noise (AWGN). These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.

However, in real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.). The models designed for AWGN would become much less effective on real noisy images.
